Manuscript_Github_Pchabaudi_pir_TPMHeatmaps

### 2021-09-02 Manuscript_pirAnalysis_Github/Pchabaudi24h/Manuscript_Github_Pchabaudi_pir_TPMHeatmaps.Rmd
Fixing chabTPMheatmap file error
Removed commented out code, and draw a heatmap that b4 was only saved

#Global save var - set to TRUE if you want to save figures.
global_save_var <- TRUE
```

@@

# pir_highest_tpm_order <- rownames(combined_data_pir_ht)

@@

# anc_ha <- rowAnnotation(foo = anno_mark(at =  na.omit(match(clade_info, 'ancestral')) , 
#                                         labels = 'ancestral',
#                                         labels_gp = gpar(fontsize = 7),
#                                         link_width = unit(3, "mm")))

ht <- Heatmap(
  log2(1+combined_data_pir_ht[,!colnames(combined_data_pir_ht) %in% 'subfam']),
  cluster_rows = FALSE,
  cluster_columns = FALSE,
  show_row_names = FALSE,
  name = 'log(TPM+1)', 
  col = colorRamp2(c(0,
                     maxcol/4,
                     maxcol/2,
                     3*maxcol/4,
                     maxcol),
                   viridis(5)),
  na_col = 'white', 
  border = TRUE,
  border_gp = gpar(lwd = 0.1),
  column_names_gp = gpar(fontsize = 10),
  row_dend_width = unit(3, "cm"),
  width = unit(4.5, 'cm'),
  height = unit(7,'cm'),
  # row_title = NULL,
  # left_annotation = clade_ha,
  # right_annotation = anc_ha,
  row_title_rot = 0,
  row_title_gp = gpar(fontsize = 10),
  row_split = forcats::fct_shift(
    relevel(
      as.factor(combined_data_pir_ht$subfam),
      ref = 'ref')
  ),
  heatmap_legend_param = list(
    labels_gp = gpar(fontsize = 10),
    title_gp = gpar(fontsize = 10,
                    fontface = 'bold'),
    at = c(0,
           maxcol/4,
           maxcol/2,
           3*maxcol/4,
           maxcol)
  )
)

@@

```{r}

@@

chapl_aapl_name_lgd <- Legend(
  title = 'CHAPL/AAPL',
  at = names(annotation_col)
    # str_subset(
    # sort(
    #   factor(chapl_aapl_name_vec,
    #          ordering(chapl_aapl_name_vec,
    #                   order_vector = 'ChAPL'))
    # )
    # ,
    # pattern = 'NA',
    # negate = TRUE
  # )
,
  legend_gp = gpar(fill = na.omit(annotation_col))
)

@@

# pir_highest_tpm_order <- rownames(combined_data_pir_ht)

#Sub-family annotation
chapl_aapl_name_info <- combined_data_pir_ht$chapl_aapl_name
annotation_col <- chapl_aapl_name_col_num[ordering(labels_chapl_aapl_name,
                                                    order_vector = 'ChAPL')]

# chapl_aapl_name_ha <- rowAnnotation(
#   'CHAPL/AAPL' = anno_simple(
#     chapl_aapl_name_info,
#     col = annotation_col,
#   ),
#   annotation_name_gp = gpar(fontsize = 10)
# )

@@

@@

# chapl_aapl_name_lgd <- Legend(
#   title = 'CHAPL/AAPL',
#   at = str_subset(
#     sort(
#       factor(labels_chapl_aapl_name,
#              ordering(labels_chapl_aapl_name,
#                       order_vector = 'ChAPL'))
#     ),
#     pattern = 'NA',
#     negate = TRUE
#   ),
#   legend_gp = gpar(fill = na.omit(annotation_col))
# )

if(global_save_var){
  pdf(file = 'Manuscript_SuppFig_ChAPL-AAPL_heatmap.pdf',
      height = 5,
      width = 5)
  draw(ht, 
       row_title_side = 'left',
       column_title_side = 'bottom',
       # heatmap_legend_side = 'right',
       # annotation_legend_side = 'right',
       # annotation_legend_list = list(chapl_aapl_name_lgd),
       # merge_legend = TRUE
  )
  dev.off()
}
```

@@

ht <- Heatmap(
  log2(1+combined_data_pir_ht[,!colnames(combined_data_pir_ht) %in% 'chapl_aapl_name']),
  cluster_rows = TRUE,
  cluster_columns = FALSE,
  show_row_names = FALSE,
  name = 'log(TPM+1)', 
  col = colorRamp2(c(0,
                     maxcol/4,
                     maxcol/2,
                     3*maxcol/4,
                     maxcol),
                   viridis(5)),
  na_col = 'white', 
  border = TRUE,
  border_gp = gpar(lwd = 0.1),
  column_names_gp = gpar(fontsize = 10),
  row_dend_width = unit(3, "cm"),
  width = unit(4.5, 'cm'),
  height = unit(7,'cm'),
  row_title = NULL,
  left_annotation = chapl_aapl_name_ha,
  # row_split = 
  #   factor(combined_data_pir_ht$chapl_aapl_name,
  #             levels = ordering(combined_data_pir_ht$chapl_aapl_name,
  #                               order_vector = 'ChAPL')),
  row_km = 9,
  heatmap_legend_param = list(
    labels_gp = gpar(fontsize = 10),
    title_gp = gpar(fontsize = 10,
                    fontface = 'bold'),
    at = c(0,
           maxcol/4,
           maxcol/2,
           3*maxcol/4,
           maxcol)
  )
)

>>>>

#Global save var - set to TRUE if you want to save figures.
global_save_var <- FALSE
```

@@

@@

ht <- Heatmap(
  log2(1+combined_data_pir_ht[,!colnames(combined_data_pir_ht) %in% 'subfam']),
  cluster_rows = FALSE,
  cluster_columns = FALSE,
  show_row_names = FALSE,
  name = 'log(TPM+1)', 
  col = colorRamp2(c(0,
                     maxcol/4,
                     maxcol/2,
                     3*maxcol/4,
                     maxcol),
                   viridis(5)),
  na_col = 'white', 
  border = TRUE,
  border_gp = gpar(lwd = 0.1),
  column_names_gp = gpar(fontsize = 10),
  row_dend_width = unit(3, "cm"),
  width = unit(4.5, 'cm'),
  height = unit(7,'cm'),
  row_title_rot = 0,
  row_title_gp = gpar(fontsize = 10),
  row_split = forcats::fct_shift(
    relevel(
      as.factor(combined_data_pir_ht$subfam),
      ref = 'ref')
  ),
  heatmap_legend_param = list(
    labels_gp = gpar(fontsize = 10),
    title_gp = gpar(fontsize = 10,
                    fontface = 'bold'),
    at = c(0,
           maxcol/4,
           maxcol/2,
           3*maxcol/4,
           maxcol)
  )
)

@@

```{r chapl_aapl_ann}

@@

chapl_aapl_name_lgd <- Legend(
  title = 'CHAPL/AAPL',
  at = names(annotation_col)
,
  legend_gp = gpar(fill = na.omit(annotation_col))
)

@@

@@

#loci annotation
chapl_aapl_name_info <- combined_data_pir_ht$chapl_aapl_name
annotation_col <- chapl_aapl_name_col_num[ordering(labels_chapl_aapl_name,
                                                    order_vector = 'ChAPL')]

@@

if(global_save_var){
  pdf(file = 'Manuscript_SuppFig_ChAPL-AAPL_heatmap.pdf',
      height = 5,
      width = 5)
  draw(ht, 
       row_title_side = 'left',
       column_title_side = 'bottom'
  )
  dev.off()
}

  draw(ht, 
       row_title_side = 'left',
       column_title_side = 'bottom'
  )
```

@@

ht <- Heatmap(
  log2(1+combined_data_pir_ht[,!colnames(combined_data_pir_ht) %in% 'chapl_aapl_name']),
  cluster_rows = TRUE,
  cluster_columns = FALSE,
  show_row_names = FALSE,
  name = 'log(TPM+1)', 
  col = colorRamp2(c(0,
                     maxcol/4,
                     maxcol/2,
                     3*maxcol/4,
                     maxcol),
                   viridis(5)),
  na_col = 'white', 
  border = TRUE,
  border_gp = gpar(lwd = 0.1),
  column_names_gp = gpar(fontsize = 10),
  row_dend_width = unit(3, "cm"),
  width = unit(4.5, 'cm'),
  height = unit(7,'cm'),
  row_title = NULL,
  left_annotation = chapl_aapl_name_ha,
  row_km = 9,
  heatmap_legend_param = list(
    labels_gp = gpar(fontsize = 10),
    title_gp = gpar(fontsize = 10,
                    fontface = 'bold'),
    at = c(0,
           maxcol/4,
           maxcol/2,
           3*maxcol/4,
           maxcol)
  )
)
